MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-24 docs/paper/out/paper.tex
add author contributions -- paper

>>>>

\section{Disclosure/Conflict-of-Interest
Statement}\label{disclosureconflict-of-interest-statement}

All authors work at the \emph{Oh no sequences!} research group, part of
Era7 Bioinformatics. Era7 offers metagenomics data analysis services
based on MG7. MG7 is open source, available under the OSI-approved
AGPLv3 license.

\section{Author Contributions}\label{author-contributions}

\begin{itemize}
\tightlist
\item
  \textbf{AA} developed \emph{MG7}, \emph{Statika}, \emph{Datasets}, and
  \emph{aws-scala-tools}; wrote the paper;
\item
  \textbf{EK} developed \emph{nispero} (a prototype for \emph{Loquat}
  \citep{kovach2014nispero}) and \emph{aws-scala-tools}.
\item
  \textbf{MM} MG7 workflow design; curation and design for the 16S-DB7
  reference database; wrote the paper.
\item
  \textbf{PPT} curation, design, data extraction code for the 16S-DB7
  reference database.
\item
  \textbf{EP} MG7 workflow design; wrote the paper.
\item
  \textbf{RT} MG7 workflow design, assignment strategy; curation and
  design for the 16S-DB7 reference database; wrote the paper.
\item
  \textbf{EPT} developed \emph{MG7}, \emph{Statika}, \emph{Datasets},
  \emph{FLASh/BLAST eDSLs}; data analysis approach and design; wrote the
  paper.
\end{itemize}

All authors have read and approved the final manuscript.
